---
title: "Exam_titanic"
author: "Meiqi Liu"
date: "2022-10-19"
output: html_document
---
# Using the titanic dataset located at "https://github.com/kijohnson/Data",  prepare an R markdown file that shows the code for a) importing the dataset, b) determining the median age for by passenger class, and c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class. Report the medians by passenger class and upload a PDF or picture of your plot

## a) importing the dataset
```{r}
# load library
pacman::p_load(readr,dplyr,ggplot2)

# import dataset
titanic<-read.csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")
```

## b) determining the median age for by passenger class
```{r}
# change to factor
titanic$Pclass<-factor(titanic$Pclass)

# get median
median<-titanic %>% 
  group_by(Pclass) %>% 
  summarise(Median=median(Age,na.rm = TRUE))
```

## c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class
```{r}
# output
png("myplot.png")

# boxplot
myplot<-ggplot(data=titanic, aes(x=Pclass, y=Age))+
  geom_boxplot()+
  labs(x="Passenger Class", y="Passenger Age", title="Boxplot")
print(myplot)
dev.off
```


