---
title: "Exam_titanic"
author: "Meiqi Liu"
date: "2022-10-19"
output: html_document
---
# Midterm Exam

## Question 3

### Using the titanic dataset located at "https://github.com/kijohnson/Data",  prepare an R markdown file that shows the code for a) importing the dataset, b) determining the median age for by passenger class, and c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class. Report the medians by passenger class and upload a PDF or picture of your plot

#### a) importing the dataset
```{r}
# load library
pacman::p_load(readr,dplyr,ggplot2)

# import dataset
titanic<-read.csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")
```

#### b) determining the median age for by passenger class
```{r}
# change Pclass to factor
titanic$Pclass<-factor(titanic$Pclass)

# get median age for by passenger class
median<-titanic %>% 
  group_by(Pclass) %>% 
  summarise(Median=median(Age,na.rm = TRUE))
# The median for passenger class 1 is 38.5;
# The median for passenger class 2 is 29.0;
# The median for passenger class 3 is 24.0;
```

#### c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class
```{r}
# output
png("myplot.png")

# boxplot for age by Passenger class
myplot<-ggplot(data=titanic, aes(x=Pclass, y=Age))+
  geom_boxplot()+
  labs(x="Passenger Class", y="Passenger Age", title="Boxplot")
print(myplot)
dev.off
```

## Question 4

### b. Next, add code to determine the percentage of males and females by class. Save this new version and push the new version to your Github repository.
```{r}
# get percentage of males and females by class
prop.table(table(titanic$Pclass,titanic$Sex),margin=1)
# In class 1, 43.5% passengers are female and 56.5% passengers are male.
# In class 2, 41.3% passengers are female and 58.7% passengers are male.
# In class 3, 29.6% passengers are female and 70.4% passengers are male.
```

